### 2018-07-02 paper/5-implementations.tex
Minor revision of S5

A \hs{Rebuilder} is a function which the \hs{Scheduler} uses to rebuild a
particular key, passing to it the key, the key's current value, and a \hs{Task}
that can compute the value of the key if necessary. It uses the persistent build
information \hs{ir} (carried by the state monad) to decide whether to rebuild
the value. If doing so is unnecessary, it returns the current value; otherwise
it runs the supplied \hs{Task} to rebuild it. In both cases it can choose to
update the persistent build information \hs{ir} to reflect what happened. So a
\hs{Rebuilder} wraps a \hs{Task}~\hs{c}~\hs{k}~\hs{v}, which unconditionally
rebuilds the key, to make a \hs{Task}~\hs{(MonadState}~\hs{ir)}~\hs{k}~\hs{v},
which rebuilds the key only if necessary, and does the necessary book-keeping.
Note that the resulting \hs{Task} is always monadic; static dependency analysis
can be performed on the original \hs{Task}~\hs{Applicative} if need be.

@@

Note that the task returned by the \hs{rebuilder} expects a total callback
function and cannot be directly executed with the partial callback \hs{fetch}.
We fix the mismatch with the function \hs{try} that relies on the standard
monad transformer \hs{ExceptT} from the \cmd{transformers} library. We also
need the \hs{liftChain} helper function, whose implementation we omit since it
is analogous to \hs{liftStore} defined in Fig.~\ref{fig-make-implementation}.

>>>>

A \hs{Rebuilder} takes three arguments: a key, its current value, and a
\hs{Task} that can (re)compute the value of the key if necessary. It uses the
persistent build information \hs{ir} (carried by the state monad) to decide
whether to rebuild the value. If doing so is unnecessary, it returns the current
value; otherwise it runs the supplied \hs{Task} to rebuild it. In both cases it
can choose to update the persistent build information \hs{ir} to reflect what
happened. So a \hs{Rebuilder} wraps a \hs{Task}~\hs{c}~\hs{k}~\hs{v}, which
unconditionally rebuilds the key, to make a
\hs{Task}~\hs{(MonadState}~\hs{ir)}~\hs{k}~\hs{v}, which rebuilds the key only
if necessary, and does the necessary book-keeping. Note that the resulting
\hs{Task} is always monadic; static dependency analysis can be performed on the
original \hs{Task}~\hs{Applicative} if needed.

@@

Note that the task returned by the \hs{rebuilder} expects a total callback
function and cannot be directly executed with the partial callback \hs{fetch}.
We fix the mismatch with the function \hs{try} that relies on the standard
monad transformer \hs{ExceptT} from the \cmd{transformers} library. We also
need the helper \hs{liftChain}, whose implementation we omit since it
is analogous to \hs{liftStore} in Fig.~\ref{fig-make-implementation}.
